%-------------------------
% Resume in Latex
% Author : Gabriel Hernandez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Load personal info if available (phone number, etc.)
% If file doesn't exist, define empty placeholder
\IfFileExists{personal_info.tex}{\input{personal_info}}{\newcommand{\myPhone}{}}

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Custom command for role headers (outdented to left margin, bold text)
\newcommand{\resumeRoleHeader}[1]{
  \vspace{6pt}
  \item[]
  \hspace{-0.15in}{\small\textbf{#1}}
  \vspace{1pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% ----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://gabreho.com/}{\Large Gabriel Hernandez}} & Email : \href{mailto:gabreho@gmail.com}{gabreho@gmail.com}\\
  \href{https://linkedin.com/in/gabreho}{linkedin.com/in/gabreho} $|$ \href{https://github.com/gabreho}{github.com/gabreho} \ifx\myPhone\empty\else & Mobile : \myPhone \fi \\
\end{tabular*}

\section{Summary}

\begin{justify}
    \small Staff Software Engineer specializing in iOS platform architecture, developer productivity, and cross-team coordination. 15+ years from co-founding full-stack startups to leading iOS platform strategy at Square, with expertise in legacy modernization and enabling large-scale engineering organizations to deliver faster and more reliably.
\end{justify}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer $\rightarrow$ Staff Software Engineer}{February 2020 -- Present}
      {Square / Block}{Toronto, ON}
      \resumeItemListStart
        \resumeRoleHeader{Staff Software Engineer / iOS Tech Lead (September 2025 -- Present)}
        \resumeItem{iOS Tech Lead for Checkout Applet Mobile team, responsible for flagship Square POS main screen across all seller verticals.}
        \resumeItem{iOS architecture expert for Converged Item Grid (evolved from Visual Browse), driving technical decisions and codebase evolution across unified POS.}
        \resumeItem{Coordinated cross-functional effort with Restaurants org (PMs, designers, engineers) to design tabs architecture expansion, ensuring future compatibility for multi-mode adoption.}

        \resumeRoleHeader{Senior Software Engineer / Retail iOS Platform Lead (March 2022 -- May 2025)}
        \resumeItem{iOS Platform Lead for Retail Mobile Engineering org (25 mobile engineers, 12 iOS engineers across 3 teams).}
        \resumeItem{Led architecture and rollout of Unified Checkout, removing 25,000+ lines of legacy code and increasing test coverage from 7\% to 50\%, contributing to iOS crash rates dropping to historical lows.}
        \resumeItem{Enabled SuperPOS launch as Retail iOS representative, implementing mode-switching and shared infrastructure abstractions to unify Square's POS apps across verticals.}
        \resumeItem{Migrated checkout navigation from brittle modal presentation logic to a structured, testable architecture, improving modularity and developer velocity.}
        \resumeItem{Created oncall runbook for Retail Mobile defining iOS and Android oncall expectations and responsibilities, coordinating with EMs and leads across 25+ engineers.}
        \resumeItem{Led Mobile Oncall Working Group across all POS teams, creating presentation materials (recorded), and coordinating automation to prevent dropped tickets in Waiting for Customers status.}

        \resumeRoleHeader{Senior Software Engineer (February 2020 -- March 2022)}
        \resumeItem{Designed and led Visual Browse iOS development, mentoring engineers and coordinating with Android and Restaurant teams to build catalog browser on shared infrastructure, now foundational to unified POS across verticals.}
        \resumeItem{Enabled Retail POS international expansion by implementing address format customizations, feature flagging for regional compliance, and adapting fulfillment workflows for multiple countries.}
      \resumeItemListEnd

    \resumeSubheading
      {Lead Mobile Developer}{September 2017 -- January 2020}
      {Skrumble Technologies}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Led mobile engineering and cross-platform coordination, managing team of developers including junior engineers and aligning technical decisions with Android lead on WebRTC protocols and messaging formats.}
        \resumeItem{Resolved critical WebRTC reliability issues in video/audio calling, redesigning VoIP connection architecture, modularizing library, and coordinating signal management across iOS and Android clients.}
        \resumeItem{Architected greenfield iOS app with blockchain capabilities, creating UI component system with "safe rails" for junior engineers, Ethereum SDK for blockchain integration, and end-to-end encryption using Signal Protocol.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Software Engineer}{October 2016 -- September 2018}
      {Girls Who Code}{Remote}
      \resumeItemListStart
        \resumeItem{Improved iOS and Android loading times by 400\% by redesigning API calls, optimizing database queries, and implementing local caches.}
        \resumeItem{Designed and implemented new timeline-based homepages for iOS and Android applications with Django API endpoints.}
        \resumeItem{Resolved critical push notification reliability issue where APNS-only approach failed to deliver content. Built Django backend with API and updated clients for guaranteed delivery.}
      \resumeItemListEnd

    \resumeSubheading
      {Co-Founder, Principal Software Engineer}{May 2013 -- December 2016}
      {GlobalMET}{Hermosillo, Mexico}
      \resumeItemListStart
        \resumeItem{Co-founded and served as Director of Technology for GlobalMET, Mexico's first coordinate-specific weather platform for rural areas, building auto-scaling distributed system on GCP processing NOAA satellite data to generate 21-day forecasts for agricultural clients across Sonora and Sinaloa.}
        \resumeItem{Engineered agricultural alert system with Django/PostgreSQL backend enabling farmers to receive automated SMS/push/email notifications when forecasts met crop-specific thresholds (frost warnings, optimal spray conditions, pest risk), improving production efficiency.}
        \resumeItem{Built full-stack platform including iOS app, macOS meteorologist tools for forecast refinement, and API infrastructure, creating disruptive innovation validated as more accurate than Weather Channel for rural Mexico.}
      \resumeItemListEnd

    \resumeSubheading
      {iOS \& Backend Engineer / Co-Founder}{January 2010 -- September 2017}
      {Big Bang Dev}{Hermosillo, Mexico}
      \resumeItemListStart
        \resumeItem{CiVO: Built full-stack VoIP and chat application (backend, iOS, Android) enabling free calls to landlines.}
        \resumeItem{UNE Transporte Sonora: Developed real-time vehicle tracking system (backend, iOS) for public transit across Sonora, Mexico.}
        \resumeItem{BuddyCard: Developed full-stack loyalty platform with Django backend/API, iOS app for venue discovery and rewards tracking, tablet app for merchant check-ins and redemptions, managing point accumulation across multiple partner businesses.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tecnológico de Monterrey}{Hermosillo, Mexico}
      {Bachelor of Science - Information and Communications Technologies (Graduated with Honors)}{Aug. 2007 -- Dec. 2011}
    \resumeSubheading
      {Concordia University}{Montreal, QC}
      {Computer Science Student Exchange Program}{Aug. 2010 -- Dec. 2010}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Swift, Objective-C} \\
     \textbf{iOS Development}{: UIKit, Blueprint, SwiftUI, Workflow} \\
     \textbf{Architecture \& Patterns}{: Protocol-Oriented Programming, Dependency Injection, Modular Architecture} \\
     \textbf{Platform Leadership}{: iOS Platform Architecture, Cross-Team Coordination, Developer Productivity, Code Quality \& Testing} \\
     \textbf{Specialized}{: WebRTC, RPC, Signal Protocol Encryption} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
